Network Cascades

### 2016-08-26 paper/paper.tex
Remove a todo that I did before
Fix some more spelling

% TODO: Explanation of the cascade window boundaries/regimes

@@

The mathematical basis for the calculations in section \ref{sec:analysis} about the cascade condition is formed by genrating functions (hence the name $G_0''(1)$ for the condition). Generating functions are a convenient tool to express series of numbers in a concise fashion. Applied to propability distributions, they allow for a convenient examination of that distribution.

>>>>

@@

The mathematical basis for the calculations in section \ref{sec:analysis} about the cascade condition is formed by generating functions (hence the name $G_0''(1)$ for the condition). Generating functions are a convenient tool to express series of numbers in a concise fashion. Applied to probability distributions, they allow for a convenient examination of that distribution.
